\input{head-1} % Load definitions and macros

\begin{document}
\ExamplesHeader{4CTa --- Combinatorics}{2}

\noindent Sometimes it is useful to make a few definitions right at the start of the example sheet,
to help out whoever is going to try follow your reasoning. Clarifying notes tend to be very helpful!
This example sheet showcases some of the features you may need when typing an example sheet.

For~$a,b\in\bbn$, with~$a\leq b$, we write~$[a,b]$
for~$\{a,a+1,\ldots,b\}$.

\smallskip


\begin{question}
Let~$k,m\in\bbn$. Prove the following assertions are equivalent:
\begin{enumerate}[(i)]
\item Whenever~\bbn\ is $k$-coloured there is a monochromatic arithmetic progression of length~$m$.
\item There exists an~$n=n(k,m)$ such that whenever~$[n]$ is $k$-coloured
      there is a monochromatic arithmetic progression of length~$m$.
\end{enumerate}
\end{question}

\begin{answer}
Here goes your beautifully-thought, and now handsomely typeset argument!
\end{answer}

\begin{intermezzo}
The next few exercises lead you towards a proof of such-and-such result.
(Use the intermezzo environment for remarks like these, which sometimes appear between exercises.)
\end{intermezzo}

\begin{question}
Given distinct~$x_1,\ldots,x_m\in\bbn$,
define~$P(x_1,\ldots,x_m)=\{\prod_{i\in I} x_i\colon I\subseteq [m],I\neq \emptyset\}$.
So~$P(x_1,\ldots,x_m)$ is the set of all products of~$x_i$.
\begin{enumerate}[(a)]
\item Determine~$P(2,3,5)$.
\item Use the finite sums theorem to prove the following.
For all~$k,m\in\bbn$ there exists an~$n'\in\bbn$ such that
whenever~$[n]$ is~$k$-coloured there are distinct~$x_1,\ldots,x_m\in[n']$
such that~$P(x_1,\ldots,x_m)$ is monochromatic.
[\emph{Hint: Let~$n$ be the number which works in the finite sums theorem.
Show that taking~$n'=2^n$ works in the statement above.
Try to find~$x_1,\ldots,x_m$ within the set~$\{2^1,2^2,\ldots,2~n\}$.}]
\end{enumerate}
\end{question}

\begin{answer}
\begin{enumerate}[(a)]
\item
  Note that\ldots
\item
  Consider\ldots
\end{enumerate}
\end{answer}

You may use the macro \cs{defi} to introduce a definition. 
For instance, a number is \defi{odd} if it is not divisible by~2.

\begin{question}
Let the~\defi{Schur number} $S(k)$ be the smallest natural number~$n$
such that every $k$-colouring of~$[n]$ contains
a~monochromatic solution to~$x+y=z$.
\begin{enumerate}[(a)]
\item Prove that~$S(k+1)\geq 3S(k) -1$.
      [\emph{Hint: Let~$c$ be a $k$-colouring of~$[N]$ such that
      there is no monochromatic solution to~$x+y=z$. Colour the blocks~$[1,N]$
      and~$[2N+2,3N+1]$ the same way as~$c$,
      and colour each number in~$[N+1,2N+1]$ by a new colour.
      Show that there is no monochromatic solution to~$x+y=z$.}]
\item Given that~$S(2)=5$, prove that~$S(k)\geq (3^k+1)/2$ for all~$k\geq 2$.
\end{enumerate}
\end{question}

\end{document}
